Cosmic web correlations with the shape, spin and peculiar velocties of dark matter halos

### 2014-01-30 paper/main.tex
new plot included in the paper

>>>>

\begin{figure*}
\includegraphics[width=0.9\textwidth]{Fig0.pdf}
\caption{Fraction of halos in a mass bin that show a preferential
  alignment with respect to an eigenvector for the three properties
  studies in this paper: shape (major axis), angular momentum and
  peculiar velocity. Left column presents the results against the Tweb
  and the right the Vweb. Strong colors refer to $256^3$ grid
  resolutions and lighter colors to a $512^3$ grid.
\label{fig:preferential}}
\end{figure*}
